Fast, Scalable Phrase-Based SMT Decoding

### 2016-06-10 acl.2016/acl2016.tex
oov penalty

As a baseline, we use a recent\footnote{as at 8th June, 2016, commit hash \scriptsize{bc5f8d15c6ce4bc678ba992860bfd4be6719cee8} } version of the Moses decoder taken from the github repository.

>>>>

As a baseline, we use a recent\footnote{The experiments were performed between January and May 2016 with the latest github code to hand. The main ar-en experiments were rerun with the source code as at 8th June, 2016 to ensure there were no material difference. The commit hash was \scriptsize{bc5f8d15c6ce4bc678ba992860bfd4be6719cee8} } version of the Moses decoder taken from the github repository.
